A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-14 dl-paper.tex
Minor change in formula

From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
\begin{multline} \label{R2_0_1-computation}
[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\beta}(b)],\ u (1 - am) \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
 \end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$. Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that
\begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
 x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha\left(\tfrac{m-\epsilon bm'}{1-am}\right). \end{multline*}
Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained from~\eqref{eq:conj-h-x} as follows:
 \begin{multline} \nonumber
 [h''] = \left[ h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
 = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].
\end{multline}
The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.
\end{proof}

>>>>

From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
\begin{multline} \label{R2_0_1-computation}
[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\beta}(b)],\ u (1 - am) \right) = \\
= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
 \end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$. Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that
\begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
 x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha\left(\tfrac{m-\epsilon bm'}{1-am}\right). \end{multline*}
Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained from~\eqref{eq:conj-h-x} as follows:
 \begin{multline} \nonumber
 [h''] = \left[ h' \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1+\tfrac{a(m-\epsilon bm')}{1-am}}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
 = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].
\end{multline}
The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.
\end{proof}
